Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-09-25 paper/numresults.tex
finish plots for Krylov-aware comparison

\begin{figure}[ht]
    \begin{minipage}[c]{.45\linewidth}
        \centering
        \input{plots/krylov_aware_density.pgf}
    \end{minipage}\hfill%
    \begin{minipage}[c]{.45\linewidth}
        %\label{tab:krylov-aware-density}
        \renewcommand{\arraystretch}{1.2}
        \begin{tabular}{@{}lccccc@{}}
        \toprule
        & $b$ & $q$ & $m$ & $n$ & $t$ (s)\\
        \midrule
        KA I & 10 & 30 & 60 & 20 & 9.13 \\
        KA II & 20 & 30 & 30 & 20 & 9.13 \\
        KA III & 10 & 60 & 30 & 40 & 9.13 \\
        KA IV & 10 & 30 & 30 & 20 & 9.13 \\
        CN++ & 10 & - & - & 20 & 9.13 \\
        \bottomrule
        \end{tabular}
        %\caption{Comparison with Krylov-Aware stochastic trace estimation.}
    \end{minipage}
    \caption{Comparison with Krylov-Aware stochastic trace estimation.}
    \label{fig:krylov-aware-density}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \input{plots/krylov_aware_spin.pgf}
    \caption{Comparison with Krylov-Aware stochastic trace estimation.}
    \label{fig:krylov-aware-spin}
\end{figure}

>>>>

\begin{figure}[ht]
    \begin{minipage}[c]{.475\linewidth}
        \centering
        \input{plots/krylov_aware_density.pgf}
    \end{minipage}\hfill%
    \begin{minipage}[c]{.475\linewidth}
        %\label{tab:krylov-aware-density}
        \vspace{-35pt}
        \input{tables/krylov_aware_density_KA.tex}
        \newline
        \newline
        \input{tables/krylov_aware_density_CN.tex}
        %\renewcommand{\arraystretch}{1.2}
        %\begin{tabular}{@{}lccccc@{}}
        %\toprule
        %& $n_{\mtx{\Omega}}$ & $n_{\mtx{\Psi}}$ & $q$ & $n$ & runtime (s)\\
        %\midrule
        %KA I & 10 & 60 & 30 & 20 & 9.13 \\
        %KA II & 20 & 30 & 30 & 20 & 9.13 \\
        %KA III & 10 & 30 & 60 & 40 & 9.13 \\
        %KA IV & 10 & 30 & 30 & 20 & 9.13 \\
        %\bottomrule
        %\end{tabular}
        %\begin{tabular}{@{}lcccc@{}}
        %\\
        %\toprule
        %& $n_{\mtx{\Omega}}$ & $n_{\mtx{\Psi}}$ & $m$ & runtime (s)\\
        %\midrule
        %CN++ & 40  & 40 & 2000 & 9.13 \\
        %\bottomrule
        %\end{tabular}
        %\caption{Comparison with Krylov-Aware stochastic trace estimation.}
    \end{minipage}
    \caption{Comparison with Krylov-Aware stochastic trace estimation.}
    \label{fig:krylov-aware-density}
\end{figure}

@@

\begin{figure}[ht]
    \begin{minipage}[c]{.475\linewidth}
        \centering
        \input{plots/krylov_aware_spin.pgf}
    \end{minipage}\hfill%
    \begin{minipage}[c]{.475\linewidth}
        \vspace{-35pt}
        \input{tables/krylov_aware_spin_KA.tex}
        \newline
        \vspace{13pt}
        \newline
        \input{tables/krylov_aware_spin_CN.tex}
    \end{minipage}
    \caption{Comparison with Krylov-Aware stochastic trace estimation.}
    \label{fig:krylov-aware-spin}
\end{figure}
